Model Averaging

### 2016-06-27 financial.rmd
started TP FP

profit <- function(df = all10mice, method = c("average","simp.log","orig.log","orig.rf","orig.boost"), 
                   seed = 300, 
                   k.folds = 5, # number of folds in initial model.blend generation
                   max.iter = 5, #max number of iterations from initial model.blend generation
                   k.folds.2 = 5, # number of folds for second step blended model development
                   tot.tests = 50 # total number of results to create
                   ){

@@

        for(m in 1:ceiling(tot.tests/max.iter)){

@@

        # create complete set
        df.blend = assemble(methods = c("log","rf","boost"), df.assem = df, x.folds.assem = 5,
                     manual.seed.assem = sample(1:1000,1))

@@

        saveit <- iter.auc(mult = max.iter/k.folds.2, x.folds.iter = k.folds.2,
                           methods = c("orig.log","average","simp.log", "orig.rf","orig.boost"),
                           df.iter = df.blend)

@@

        # saveRDS(compile.results, "C:/Users/n9232371/Documents/github/consult/finalwriteup/report_data/finance_results.rds")
        # compile.results <- readRDS("C:/Users/n9232371/Documents/github/consult/finalwriteup/report_data/finance_results.rds")

        ####
        # now have a suite of predictions - merge with original all10.blend$balance.mlsto
        df.blend$index = rownames(df.blend) %>% as.numeric
        # load balances
        all6 <-read.csv('C:/Users/n9232371/OneDrive/shared files/Bligh Tanner/masters/data/all6.csv')
        all6 <- all6 %>% select(mlsto, balance.mlsto) %>% distinct()
        all6$mlsto <- as.character(all6$mlsto)
        df.blend = left_join(df.blend, all6)
        compile.results <- map(compile.results, function(x) 
                left_join(x, df.blend %>% select(index, balance.mlsto, b.rpdol)))

@@

@@

@@

# saveRDS(plot.results,"C:/Users/n9232371/Documents/github/consult/finalwriteup/report_data/plot_finance.rds" )

@@

@@

simp.l <- compile.results[['average']]
simp.l$mean.iter <- rowMeans(simp.l[,2:11])

saveRDS(simp.l, "C:/Users/n9232371/Documents/github/consult/finalwriteup/report_data/finance_average_model.rds")

>>>>

profit <- function(df = all10mice, method = c("average","simp.log","simp.boost","orig.log","orig.rf","orig.boost"), 
                   seed = 400, 
                   k.folds = 5, # number of folds in initial model.blend generation
                   max.iter = 5, #max number of iterations from initial model.blend generation
                   k.folds.2 = 5, # number of folds for second step blended model development
                   tot.tests = 500 # total number of results to create
                   ){

@@

        #store results of three original models in list for each iteration
        joined <- assemble(methods = c("log", "rf", "boost"), df.assem = df, x.folds.assem = 5,
                    iterations = ceiling(tot.tests/k.folds.2))

        # saveRDS(joined, "/Users/yam/Documents/github/consult/finalwriteup/report_data/joined.rds")
        # run blended models on each of the 100 outputs from original models stored
        # in joined list. Store as new list 'compile.results' for each blending method
        for(m in 1:ceiling(tot.tests/max.iter)){

@@

        # create complete set using mth list item in joined
        df.blend = full_join(df %>% mutate(rown = 1:nrow(df)), joined[[m]], 
                                by = c('rown'='rownames'))
        df.blend <- df.blend %>% select(-rown)

        # df.blend = assemble(methods = c("log","rf","boost"), df.assem = df, x.folds.assem = 5)

@@

        # saveRDS(df.blend, "C:/Users/n9232371/Documents/github/consult/dfblend.rds")
        # df.blend <- readRDS("/Users/yam/Documents/github/consult/dfblend.rds")

        saveit <- iter.auc(mult = max.iter/k.folds.2, x.folds.iter = k.folds.2,
                           methods = c(
                                  # "simp.log","average",
                                  # "orig.log","orig.rf","orig.boost",
                                  # "comp.rf","comp.boost","FWLS",
                                   "simp.boost"
                                  ),
                           df.iter = df.blend)

@@

        # saveRDS(compile.results, "/Users/yam/Documents/github/consult/finalwriteup/report_data/finance_results_simpboost.rds")
        # compile.results <- readRDS("C:/Users/n9232371/Documents/github/consult/finalwriteup/report_data/finance_results.rds")

        ####
        # now have a suite of predictions - merge with original all10.blend$balance.mlsto
        df.blend$index = rownames(df.blend) %>% as.numeric
        # load balances
        all6 <-read.csv('C:/Users/n9232371/OneDrive/shared files/Bligh Tanner/masters/data/all6.csv')
        #iOS
        all6 <-read.csv('/Users/yam/OneDrive/shared files/Bligh Tanner/masters/data/all6.csv')
        all6 <- all6 %>% select(mlsto, balance.mlsto) %>% distinct()
        all6$mlsto <- as.character(all6$mlsto)
        df.blend = left_join(df.blend, all6)
        compile.results <- map(compile.results, function(x) 
                left_join(x, df.blend %>% select(index, balance.mlsto, b.rpdol)))

@@

        # set up list of blank dataframes for profit calcs for each iteration: prof.results
        colnames = names(compile.results[[1]])[grepl('iter', names(compile.results[[1]]))]
        new.df = matrix(NA, nrow = length(threshold), ncol = ceiling(tot.tests/max.iter) + 1) %>% as.data.frame
        colnames(new.df) <- c('threshold', colnames)
        new.df$threshold = threshold 
        prof.results = list(new.df)
        names(prof.results) = names(compile.results)

@@

#function below assigns results to 'prof.results' object in global env
profit(df = all10mice, method = c("average","simp.log",'simp.boost', "orig.log","orig.rf","orig.boost"),
                   seed = 300,
                   k.folds = 5, # number of folds in initial model.blend generation
                   max.iter = 5, #max number of iterations from initial model.blend generation
                   k.folds.2 = 5, # number of folds for second step blended model development
                   tot.tests = 500 # total number of results to create
                   )

@@

saveRDS(plot.results,"C:/Users/n9232371/Documents/github/consult/finalwriteup/report_data/plot_finance_100_3.rds" )
saveRDS(plot.results,"/Users/yam/Documents/github/consult/finalwriteup/report_data/plot_finance_100_3.rds" )

bind <- bind %>% filter(!method %in% 'FWLS')
bind <- rbind(bind, plot.results)

@@

Check for significant difference between samples

```{r t_test}
plot.results

index = c(2:8)
pvals = data.frame("method" = levels(plot.results$method %>% as.factor)[c(2:8)], 
                   "threshold" = 
                   'p_value' = NA)
for(i in seq_along(index)){
        pvals$p_value[i] = t.test(auc.150[[1]], 
                                  auc.150[[index[i]]])$p.value %>%
                format(digits = 2) %>% as.numeric
}

@@

simp.l <- compile.results[['simp.log']]
simp.l$mean.iter <- rowMeans(simp.l[,2:101])

saveRDS(simp.l, "/Users/yam/Documents/github/consult/finalwriteup/report_data/finance_average_model.rds")

### 2016-06-27 model_blend.rmd
started TP FP

#setwd in onedrive data
write.csv(all10.blend, '~/OneDrive/shared files/Bligh Tanner/masters/data/all10blend.csv')
# write.csv(all10.blend, 'all10blend2.csv')
# all10.blend<- read.csv('all10blend2.csv')
# ensure levels in correct order:
all10.blend$f.rpdol =  factor(all10.blend$f.rpdol, levels= c("profit", "loss"))

@@

@@

formula.log <- "f.rpdol ~ b.timespan.cbrt + no.users + b.inv.log + Business + JD.Second + norm.log + norm.rf + norm.boost"

@@

#formula to add interaction terms for logistic regression
metafeatures = strsplit(formula.log, split = c("\\s\\~\\s|\\s\\+\\s"))[[1]]
methods = metafeatures[7:9]
metafeatures = metafeatures[2:6]

for(j in seq_along(methods)){
        for(m in seq_along(metafeatures)){
                formula.log <- paste(formula.log, " + ", metafeatures[m], "*", methods[j], sep = "")
        }
}

@@

iter.auc(mult = 20, x.folds = 5, seedy = 100, df = all10.blend,
         methods = c("orig.log","log","average", "boost","rf", "simp.log","simp.boost"))
# iter.auc(mult = 20, x.folds = 5, seedy = 100, df = all10.blend,
#          methods = c("simp.log", "average"))
# 
# no.boost <- auc.list
# saveRDS(auc.list, "/Users/yam/Documents/github/consult/finalwriteup/report_data/blend_auc.rds")
auc.list <- readRDS("C:/Users/n9232371/Documents/github/consult/finalwriteup/report_data/blend_auc.rds")
# auc.list <- append(auc.list, no.boost)
# names(auc.list)[c(8,9)] = c("simp.log.noboost","average.noboost")
#don't worry about simp.log.notrans  - transformation of model predictions doesn't improve results at all

>>>>

#setwd in onedrive data
write.csv(all10.blend, '~/OneDrive/shared files/Bligh Tanner/masters/data/all10blend2.csv')
# all10.blend <- read.csv('~/OneDrive/shared files/Bligh Tanner/masters/data/all10blend2.csv')[,-1]
# write.csv(all10.blend, 'all10blend2.csv')
# all10.blend<- read.csv('all10blend2.csv')
# ensure levels in correct order:
all10.blend$f.rpdol =  factor(all10.blend$f.rpdol, levels= c("profit", "loss"))

@@

Now narrow down which interaction terms to include
```{r}
fit2 <- aov(b.rpdol ~ b.timespan.cbrt + no.users + b.inv.log + Business + JD.Second + norm.log + norm.rf + norm.boost + b.timespan.cbrt*norm.log + no.users*norm.log + b.inv.log*norm.log + Business*norm.log + JD.Second*norm.log + b.timespan.cbrt*norm.rf + no.users*norm.rf + b.inv.log*norm.rf + Business*norm.rf + JD.Second*norm.rf + b.timespan.cbrt*norm.boost + no.users*norm.boost + b.inv.log*norm.boost + Business*norm.boost + JD.Second*norm.boost + Discipline*norm.boost + Discipline*norm.log + Discipline*norm.rf,
                                   data = all10.blend)

@@

formula.log <- "f.rpdol ~ norm.log + norm.rf + norm.boost + b.timespan.cbrt*norm.log + b.inv.log*norm.log + b.inv.log*norm.rf + Business*norm.boost"

@@

@@

iter.auc(mult = 20, x.folds = 5, seedy = 100, df = all10.blend,
         methods = c("orig.log","log","average", "comp.boost","comp.rf", "simp.log","simp.boost"))
iter.auc(mult = 20, x.folds = 5, seedy = 100, df = all10.blend,
         methods = c("log"))
# iter.auc(mult = 20, x.folds = 5, seedy = 100, df = all10.blend,
#          methods = c("simp.log", "average"))
# 
# no.boost <- auc.list
saveRDS(auc.list, "/Users/yam/Documents/github/consult/finalwriteup/report_data/blend_auc.rds")
auc.list <- readRDS("/Users/yam/Documents/github/consult/finalwriteup/report_data/blend_auc1.rds")
# auc.list <- append(auc.list, no.boost)
# names(auc.list)[c(8,9)] = c("simp.log.noboost","average.noboost")
#don't worry about simp.log.notrans  - transformation of model predictions doesn't improve results at all
